On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-22 Manuscript/manuscript.tex
inserted missing negative sign in conclusion

\jy{use a better topic sentence.}
When using Student's $t$ intervals and $\phi$ is unknown, the results of this
study suggest that an $n \geq 800$ may be necessary for common practice to
estimate simpler parameters like $\mu$ or $\sigma_x$. If $\phi$ is already
known, a lesser $n$ may be adequate to estimate these parameters. For lower
absolute values of $\phi$, a smaller $n$ is sufficient when estimating $\mu$
or $\sigma$. For negative values of $\phi$, coverage of $\mu$ is higher in
general. In fact, Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$
when using smaller sample sizes, meaning that if $\phi$ is known to have a
very negative value, another CI may be required. However, in real world
applications, $\phi$ is more commonly found to be positive, so Student's $t$
should still be used if $\phi$ is unknown. Lastly, to estimate $\phi$,
$n \geq 100$ using the Student's $t$ method may be sufficient. Further
investigation may be necessary to see if there are other interval corrections
that fix the coverage deterioration problem for $\phi$.

>>>>

\jy{use a better topic sentence.}
When using Student's $t$ intervals and $\phi$ is unknown, the results of this
study suggest that an $n \geq 800$ may be necessary for common practice to
estimate simpler parameters like $\mu$ or $\sigma_x$. If $\phi$ is already
known, a lesser $n$ may be adequate to estimate these parameters. For lower
absolute values of $\phi$, a smaller $n$ is sufficient when estimating $\mu$
or $\sigma$. For negative values of $\phi$, coverage of $\mu$ is higher in
general. In fact, Student's $t$ seems to over-cover $\mu$ for $\phi = - 0.4$
when using smaller sample sizes, meaning that if $\phi$ is known to have a
very negative value, another CI may be required. However, in real world
applications, $\phi$ is more commonly found to be positive, so Student's $t$
should still be used if $\phi$ is unknown. Lastly, to estimate $\phi$,
$n \geq 100$ using the Student's $t$ method may be sufficient. Further
investigation may be necessary to see if there are other interval corrections
that fix the coverage deterioration problem for $\phi$.
